%%%%%%%%%%%%%%%%% DO NOT CHANGE HERE %%%%%%%%%%%%%%%%%%%% {
    \documentclass[12pt,a4]{article}
    \usepackage{fullpage}
    \usepackage[top=2cm, bottom=4.5cm, left=2.5cm, right=2.5cm]{geometry}
    \usepackage{amsmath,amsthm,amsfonts,amssymb,amscd}
    \usepackage{lastpage}
    \usepackage{enumerate}
    \usepackage{fancyhdr}
    \usepackage{mathrsfs}
    \usepackage{xcolor}
    \usepackage{graphicx}
    \usepackage{listings}
    \usepackage{hyperref}
    \usepackage{titlesec}
    \usepackage{amsfonts}

    \titleformat{\subsection}[runin]
  {\normalfont\large\bfseries}{\thesubsection}{1em}{}

  \titleformat{\subsubsection}[runin]
  {\normalfont\small}{\thesubsubsection}{1em}{}
    
    \hypersetup{%
      colorlinks=true,
      linkcolor=blue,
      linkbordercolor={0 0 1}
    }
    
    \setlength{\parindent}{0.0in}
    \setlength{\parskip}{0.05in}
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% }
    
    %%%%%%%%%%%%%%%%%%%%%%%% CHANGE HERE %%%%%%%%%%%%%%%%%%%% {
    \newcommand\course{MATH 111-X}
    \newcommand\semester{2nd Sem, 23-24}
    \newcommand\hwnumber{2}                 % <-- ASSIGNMENT #
    \newcommand\NetIDa{John Onesimus G. Ancheta}           % <-- YOUR NAME
    \newcommand\NetIDb{202067240}           % <-- STUDENT ID #
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% }
    
    %%%%%%%%%%%%%%%%% DO NOT CHANGE HERE %%%%%%%%%%%%%%%%%%%% {
    \pagestyle{fancyplain}
    \headheight 35pt
    \lhead{\NetIDa}
    \lhead{\NetIDa\\\NetIDb}                 
    \chead{\textbf{\large Problem Set \hwnumber}}
    \rhead{\course \\ \semester}
    \lfoot{}
    \cfoot{}
    \rfoot{\small\thepage}
    \headsep 1.5em
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% }
    
\begin{document}

\subsection*{1} Let $\star$ be defined on $\mathbb{Z}$ by letting $a \star b = ab$. Verify whether $(\mathbb{Z}, \star)$ is a group by checking whether it satisfy the 3 group axioms. \\ \\
\textit{Solution}:\\
Observe that in our description, the operation $\star$ is already defined on $\mathbb{Z}$, hence we only need to show the 3 group axioms.

\begin{itemize}
\item Suppose $c \in \mathbb{Z}$. Thus we have $(a \star b) \star c = (a \cdot b) \cdot c = abc$; as well as $a \star (b \star c) = a \cdot (b \cdot c) = abc$. Hence $\star$ is associative.  
\item Now, consider \(e \in \mathbb{Z}\, \text{where } e=1\). Hence for any integer we have: \(a \star e = ae = a \), as well as \(e  \star a = ea = a\). Hence, there exists an identity element for the operation \(\star\). 
\item Finally, let \(a^{-1}, b^{-1} \in \mathbb{Z}\). By definition of an inverse we have, \(a^{-1} \star  a = a^{-1}a = e\), as well as \(b^{-1} \star  b = b^{-1}b = e\). Since for any \(a,b \in \mathbb{Z} \, , \, a\star b=ab=ba=b\star a \), this operation is also commutative. And hence, the right hand inverse of \(a \, , b\) should also follow. 
\end{itemize}

Since the binary operation \(\star \) satisfies all three group axioms, therefore \( \mathbb{Z}, \star \) is a group. \( \square   \) 

\subsection*{2} Let $\star$ be defined on $2\mathbb{Z} = \{ 2n\, | \,n \in \mathbb{Z} \}$ by letting $a \star b = a + b$. Verify whether $(2\mathbb{Z}, \star)$ is a group as in the item above. 







\subsection*{3} Let $G$ be a group and suppose that $(ab)^2=a^2b^2$ for all $a$ and for all $b$ in $G$. Prove that $G$ is an abelian group.
\begin{proof}
  Since \(G\) is defined as a group we have: \(a^{2}b^{2}=a a b b\). Multiplying the left by \(a^{-1}\) and the right by \(b^{-1}\) we get: 
  \(a^{-1} a a b b = a a b b b^{-1}\ \Rightarrow ab^{2} = a^2 b \)     
\end{proof}

\subsection*{4} Let $\{ H_i \}_{i \in I}$ be an arbitrary collection of subgroups of a group $G$ for some index set $I$, show that $\bigcap\limits_{i \in I} H_{i}$ is a subgroup of $G$. Is  $\bigcup\limits_{i \in I} H_{i}$ a subgroup of $G$? Justify your claims.

\subsection*{5} Let $G$ be an abelian group. Show that the elements of finite order in $G$ form a subgroup. This subgroup
is called the torsion subgroup of $G$.

\subsection*{6} Let S be any subset of group $G$.

    \subsubsection*{(a)} Show that $H_{s} = \{ x \in G | xs=sx \text{ for all } s \in S\}$ is a subgroup of $G$.

    \subsubsection*{(b)} Show that $H_{G}$ is an abelian group, where $H_{G}$ is called the center of $G$.

\subsection*{7} List all of the elements in each of the following subgroups and draw the lattice diagram$^\star$ as needed.

    \subsubsection*{(a)} The subgroup of $\mathbb{Z}_{24}$ generated by $15$

    \subsubsection*{(b)} All subgroups $\mathbb{Z}_{48} \text{\textit{ draw lattice here }}$

    \subsubsection*{(c)} The subgroup generated by $5$ in $U(18) =(\mathbb{Z}_{18})^{\times}$










\end{document}
